---
title: "Landing Page Version 4.0 using current_url"
author: "Sajad Ghashami"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
   html_document:
     code_folding: hide
     theme: cerulean
---

```{=html}
<style type="text/css">
.main-container {
  max-width: 1400px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align = 'center')
```

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(DBI)
library(rmarkdown)
library(ggpubr)
library(data.table)
library(knitr)
library(plotly)
library(rsconnect)
library(reactable)
library(moments)
library(downloadthis)
library(DT)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
con <- DBI::dbConnect(odbc::odbc(),
                      #Snowflake
                      #SnowflakeDSIIDriver
                      Driver       = "SnowflakeDSIIDriver",
                      Server       = "ed87949.us-east-1.snowflakecomputing.com",
                      UID          = "SHINY_APP",
                      PWD          =  "5UK@cMGTf2xA",
                      
                      # UID          = rstudioapi::askForPassword("Database user"),
                      # PWD          = rstudioapi::askForPassword("Database password"),
                      Database     = "EDW",
                      Warehouse    = "shiny_app",
                      Schema       = "dim"
                      #,
                      #authenticator = "externalbrowser"
                      )
mywh <- DBI::dbSendQuery(con, 'use role shiny_app_role')
#mywh <- DBI::dbSendQuery(con, 'use role developer_role')
mywh <- DBI::dbSendQuery(con, 'use warehouse shiny_app')
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
top <- DBI::dbGetQuery(con,
"
SELECT * 
FROM ANALYTICS.SANDBOX.landing_page_top_current_url
     ")

```

## Query to create the historical Path

Click `Code/Hide` to Show/hide it

```{r eval=FALSE}
"
CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_base_third_version_2023_06_02 AS
WITH all_records AS (
    
    SELECT
        event_name,
        event_type,
        description,
        es.user_id,
        es.date_created,
        es.object_id,
        CASE 
        WHEN es.path LIKE '/read/%' THEN '/read/'
        ELSE es.path
        END
        AS new_path,
        es.date_created AS session_timestamp
    FROM data_hub.kinesis.event_stream es
    -- etl.user_id_merges and data_hub.etl.user_id_merges suddenly stopped working so I am using EDW_STAGING_DEVELOPMENT
        LEFT JOIN EDW_STAGING_DEVELOPMENT.STAGING.USER_ID_MERGES  uim ON uim.from_user_id = es.user_id 
        JOIN dim.users u ON u.user_id = COALESCE(uim.to_user_id, es.user_id)
    WHERE es.user_id IS NOT NULL
         AND es.date_created >= '2023-01-01'
         AND es.date_created < current_date()         
         AND es.path IS NOT NULL
         AND es.event_name='Page View'
         AND u.is_teacher= TRUE

         
)
, engagement_intervals AS (
    SELECT
        al.event_name,
        al.event_type,
        al.description,
        al.user_id,
        al.date_created,
        al.new_path,
        al.session_timestamp,
        (extract(epoch from session_timestamp) - lag(extract(epoch from session_timestamp)) OVER (PARTITION BY user_id ORDER BY session_timestamp))/60 AS minutes_since_last_interval,
        CASE WHEN extract(epoch FROM session_timestamp) - lag(extract(epoch FROM session_timestamp)) OVER (PARTITION BY user_id ORDER BY session_timestamp) > 30 * 60 THEN 1 ELSE 0 END AS new_event_boundary
    FROM   all_records AS al
        
)

    SELECT
        ei.event_name,
        ei.event_type,
        ei.description,
        ei.user_id,
        ei.date_created,
        ei.new_path as path,
        ei.session_timestamp,
        SUM(new_event_boundary) OVER (PARTITION BY user_id ORDER BY session_timestamp) AS session_number,
        user_id || '-' || cast(SUM(new_event_boundary) OVER (PARTITION BY user_id ORDER BY session_timestamp) AS varchar) AS session_id
    FROM engagement_intervals ei

    
-----------------------------------------------------------------------------------        
CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_top_exit_page_base_third_version_2023_06_02  AS
WITH initial AS (
SELECT 
      session_id,
      user_id,
      path,
      session_timestamp,
      ROW_NUMBER() OVER (PARTITION BY session_id ORDER BY session_timestamp DESC) AS  path_order
FROM ANALYTICS.SANDBOX.landing_page_base_third_version_2023_06_02
WHERE path IS NOT NULL    
ORDER BY 1,2,3,4, 5
)
SELECT path AS last_url,
       TO_DATE(session_timestamp) AS date, 
       COUNT(*) AS frequency
FROM initial
WHERE path_order=1
GROUP BY path,
         date



---------------------------------------------------------------------------------------
CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_top_exit_page_third_version_2023_06_02 AS
SELECT last_url,
       SUM(frequency) AS total,
       RANK() OVER (ORDER BY total DESC) AS rank_number
FROM ANALYTICS.SANDBOX.landing_page_top_exit_page_base_third_version_2023_06_02
GROUP BY last_url

-----------------------------------------------------------------------------
CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_top_exit_page_daily_2023_06_02 AS
SELECT exit_base.*,
       exit_top.rank_number
FROM ANALYTICS.SANDBOX.landing_page_top_exit_page_base_third_version_2023_06_02 AS exit_base
JOIN (SELECT * FROM ANALYTICS.SANDBOX.landing_page_top_exit_page_third_version_2023_06_02 WHERE rank_number <= 10) AS exit_top
     ON exit_base.last_url= exit_top.last_url





CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_all_2023_06_02 AS
-- To include only top 1000 URLs 
WITH top_paths AS (
SELECT path,
       COUNT(*)
FROM ANALYTICS.SANDBOX.landing_page_base_third_version_2023_06_02
WHERE path is not NULL
GROUP BY path
ORDER BY COUNT(*) DESC
LIMIT 1000
)
, transformed AS (
SELECT
        session_number||user_id||TO_DATE(date_created) AS session_id,
        es.user_id,
        es.path,
        TO_DATE(es.date_created) AS session_date,
        MIN(session_timestamp) AS session_start_timestamp,
        MAX(session_timestamp) AS session_end_timestamp,
        DATEDIFF(second, MIN(session_timestamp), MAX(session_timestamp)) AS product_engagement_time_seconds,
        DATEDIFF(minute, MIN(session_timestamp), MAX(session_timestamp)) AS product_engagement_time_minutes
    FROM
        ANALYTICS.SANDBOX.landing_page_base_third_version_2023_06_02 es
    WHERE path IS NOT NULL    
    GROUP BY
        1,2,3,4
)
-- Have to trunc the text because LISTAGG does not accept long texts: Error: String '(LISTAGG result)' is too long and would be truncated
, truncated AS (
SELECT       
       session_id,       
       user_id,
       CASE WHEN LENGTH(path) > 30
                      THEN LEFT(path, 30) || '...'
                      ELSE path
                      END AS truncated_path,
       session_start_timestamp,
       product_engagement_time_seconds
       
FROM transformed
WHERE path IS NOT NULL
      AND path IN (SELECT path FROM top_paths)
)
, base AS (
SELECT       
       session_id,       
       user_id,
       MIN(TO_DATE(session_start_timestamp)) AS session_start_date,
       listagg(truncated_path , ', ') WITHIN GROUP (ORDER BY session_start_timestamp ASC) AS all_paths,
       listagg(truncated_path , ', ') WITHIN GROUP (ORDER BY session_start_timestamp DESC) AS all_paths_exit,
       SUM(product_engagement_time_seconds) AS total_spent_time
       
FROM truncated      
GROUP BY       
       session_id,       
       user_id    
 )
SELECT 
      session_start_date,
      all_paths,
      all_paths_exit,
      SUM(total_spent_time) AS total_time_spent_in_seconds,
      COUNT(*) AS FREQUENCY
FROM base      
GROUP BY
      session_start_date,
      all_paths,
      all_paths_exit
ORDER BY COUNT(*) DESC       



-------------------------------------------------------------
CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_top_2023_06_02 AS
SELECT all_paths,
       SUM(FREQUENCY) AS total,
       SUM(total_time_spent_in_seconds) AS duration_in_seconds,
       RANK() OVER (ORDER BY total DESC) AS rank_number
FROM  ANALYTICS.SANDBOX.landing_page_all_2023_06_02
GROUP BY all_paths
ORDER BY total DESC


------------------------------------------------------------------
CREATE OR REPLACE TABLE ANALYTICS.SANDBOX.landing_page_top_daily_2023_06_02 AS
SELECT land_base.*,
       land_top.rank_number
FROM ANALYTICS.SANDBOX.landing_page_all_2023_06_02 AS land_base
JOIN (SELECT * FROM ANALYTICS.SANDBOX.landing_page_top_2023_06_02 WHERE rank_number <= 10) AS land_top
     ON land_base.all_paths= land_top.all_paths

     "
```

## Top Paths (Total)

Notes: <br>
1- Only top URL(path) are chosen the rest are excluded (Even if existed in All_Path) <br>
2- If a URL has more than 30 characters then you only see the top 30 characters followed by `...`<br>
3- It capture data after 2023-01-01

```{r, out.width = "100%"}
top %>%
  mutate(Duration_to_Frequency= round(DURATION_IN_SECONDS/TOTAL,2)) %>%
  select(RANK_NUMBER, everything()) %>%
  arrange(desc(-RANK_NUMBER)) %>%
  slice(1:100) %>%
  select(RANK_NUMBER, everything()) %>%
  datatable()

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
top_daily <- DBI::dbGetQuery(con,
"
SELECT * 
FROM ANALYTICS.SANDBOX.landing_page_top_current_url_daily
     ")

```

## Top Paths (Total) - Daily Trends

Note: We are showing the trends for only top 10 overall frequent paths


## Top Paths (Total) - Daily Trends Bar Chart

```{r , out.width = "100%",  fig.height= 30}
top_daily$Full_path <- reorder( top_daily$ALL_PATHS, top_daily$RANK_NUMBER)
chart <- ggplot(top_daily,
                aes(x = SESSION_START_DATE, y = FREQUENCY, fill=ALL_PATHS,), color = "black") +
  geom_bar(stat = "identity") +
  facet_wrap(. ~ Full_path, ncol=1, labeller = label_both, scales = "free_y") +
  labs(x = "SESSION START DATE", y = "Frequency") +
  theme(panel.spacing = unit(4, "lines")) +
  theme(legend.position="top")


plotly_obj <- ggplotly(chart) %>% 
  layout(
    legend = list(
      orientation = 'h', x = 0.3, y = -0.1, 
      title = list(text = 'Path')
      )
    )

plotly_obj
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
top_exit <- DBI::dbGetQuery(con,
"
SELECT * 
FROM ANALYTICS.SANDBOX.landing_page_top_exit_page_current_url
     ")

```

## Top Last URLs (Total)

```{r, out.width = "100%"}
top_exit %>%
  arrange(desc(-RANK_NUMBER)) %>%
  slice(1:100) %>%
  select(RANK_NUMBER, LAST_URL, TOTAL) %>%
  datatable()

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
top_daily_exit <- DBI::dbGetQuery(con,
"
SELECT * 
FROM ANALYTICS.SANDBOX.landing_page_top_exit_page_current_url_daily
     ")

```




## Top Last URLs (Total) -Dailt Trends

```{r , out.width = "100%",  fig.height= 30}
top_daily_exit$LAST_URL <- reorder( top_daily_exit$LAST_URL, top_daily_exit$RANK_NUMBER)
chart <- ggplot(top_daily_exit,
                aes(x = DATE, y = FREQUENCY, fill=LAST_URL,), color = "black") +
  geom_bar(stat = "identity") +
  facet_wrap(. ~ LAST_URL, ncol=1, labeller = label_both, scales = "free_y") +
  labs(x = "SESSION START DATE", y = "Frequency") +
  theme(panel.spacing = unit(4, "lines"))


plotly_obj <- ggplotly(chart) %>% 
  layout(
    legend = list(
      orientation = 'h', x = 0.3, y = -0.1, 
      title = list(text = 'Exit Path')
      )
    )

plotly_obj
```
